\Title

### 2016-08-18 manuscript/manuscript.tex
Started discussion section explaining why andes is wrong
Fixes #32

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Discussion}

Differences between our Moho depth model and the seismological data
(shown in Fig.~\ref{fig:sam-residuals}b)
may indicate regions where our initial assumptions
(summarized in Fig.~\ref{fig:anomalysketch})
are inadequate or where we have
failed to correct for all crustal and mantle sources.
In general, our model fits both the seismological and gravity data well
in the oceans and in the Atlantic coast.
The largest differences are seen the along the Andean Province.
These differences are likely caused by the fact that our model does not include
the subducting Nazca plate.
Furthermore, the CRUST1.0 synthetic data test (Fig.~\ref{fig:crust1-results})
suggests that our inversion method is not able to fully recover deep Moho
depths in the Andes,
even without the effect of the subducting plate.
